ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-28 doc/paper.tex
lit shuffling

Although a number of open-source projects which interface other languages with SuperCollider exist
\cite{systemsinterfacingwithsc,magnusson2011ixi,orlarey2009faust}, they are mostly SuperCollider
clients, which have features to control synths and send other automation messages. One notable
exception is OctaveSC~\cite{octavesc}, which embeds GNU Octave within SuperCollider. However, it
is designed for performing operations on control rate data arrays and suffers from performance
issues which prevent it from being used on audio rate data.

@@

@@

Although the interface and granularity of SPEAR differs significantly from those in project, the
techniques for high quality resynthesis presented should prove useful for improving the quality of
the sound output.

>>>>

Although a number of open-source projects which interface other languages with SuperCollider exist
\cite{systemsinterfacingwithsc,magnusson2011ixi,orlarey2009faust}, they are mostly SuperCollider
clients, which have features to control synths and send other automation messages. One notable
exception is OctaveSC~\cite{octavesc}, which embeds GNU Octave within SuperCollider. However, it
is designed for performing operations on control rate data matrices and suffers from performance
issues which prevent it from being used on audio rate data.

@@

Although the interface and granularity of SPEAR differs significantly from those in ScPy, the
techniques for high quality resynthesis presented should prove useful for improving the quality of
the sound output.

@@
